Shiny App Manuscript Figures: Aquatic Organisms

### 2022-01-08 App_Nonessential/TeamX_Manuscript_Figures/Manuscript_Figures_TeamX.Rmd
team x manuscript figures

#Import packages
library(tidyverse) 
library(wesanderson)

#Import Data
aoc <- read_csv("AquaticOrganisms_Clean_final.csv", guess_max = 10000)

#Data Tidying
# Master dataset for scatterplots - for Heili's tab.
aoc_v1 <- aoc %>% # start with original dataset
   # full dataset filters.
  mutate(effect_f = factor(case_when(effect == "Y" ~ "Yes",
    effect == "N" ~ "No"),
    levels = c("No", "Yes"))) %>%
  # removing NAs to make data set nicer
  replace_na(list(size.category = 0, shape = "Not Reported", polymer = "Not Reported", life.stage = "Not Reported", chem.exp.typ.nominal = "Particle Only"))

aoc_setup <- aoc_v1 %>% # start with original dataset
  mutate(size_f = factor(case_when(
    size.category == 1 ~ "1nm < 100nm",
    size.category == 2 ~ "100nm < 1µm",
    size.category == 3.1 ~ "1µm < 10µm",
    size.category == 3.2 ~ "10µm < 100µm",
    size.category == 4 ~ "100µm < 1mm",
    size.category == 5 ~ "1mm < 5mm",
    size.category == 0 ~ "Not Reported"),
    levels = c("1nm < 100nm", "100nm < 1µm", "1µm < 10µm", "10µm < 100µm", "100µm < 1mm", "1mm < 5mm", "Not Reported"))) %>% # creates new column with nicer names and order by size levels.
  # shape category data tidying.
  mutate(shape_f = factor(case_when(
    shape == "fiber" ~ "Fiber",
    shape == "fragment" ~ "Fragment",
    shape == "sphere" ~ "Sphere",
    shape == "Not Reported" ~ "Not Reported"),
    levels = c("Fiber", "Fragment", "Sphere", "Not Reported"))) %>% # order our different shapes.
  # polymer category data tidying.
  mutate(poly_f = factor(case_when(
    polymer == "BIO" ~ "Biopolymer",
    polymer == "EVA" ~ "Polyethylene Vinyl Acetate",
    polymer == "LTX" ~ "Latex",
    polymer == "PA" ~ "Polyamide",
    polymer == "PE" ~ "Polyethylene",
    polymer == "PC" ~ "Polycarbonate",
    polymer == "PET" ~ "Polyethylene Terephthalate",
    polymer == "PI" ~ "Polyisoprene",
    polymer == "PMMA" ~ "Polymethylmethacrylate",
    polymer == "PP" ~ "Polypropylene",
    polymer == "PS" ~ "Polystyrene",
    polymer == "PUR" ~ "Polyurethane",
    polymer == "PVC" ~ "Polyvinylchloride",
    polymer == "PLA" ~ "Polylactic Acid",
    polymer == "Not Reported" ~ "Not Reported"))) %>%
  # taxonomic category data tidying.
  mutate(org_f = factor(organism.group, levels = c("Algae", "Annelida", "Bacterium", "Cnidaria", "Crustacea",
                                                   "Echinoderm", "Fish", "Insect", "Mollusca", "Nematoda", "Plant", "Rotifera", "Mixed"))) %>% # order our different organisms.
  mutate(lvl1_f = factor(case_when(lvl1 == "alimentary.excretory" ~ "Alimentary, Excretory",
    lvl1 == "behavioral.sense.neuro" ~ "Behavioral, Sensory, Neurological",
    lvl1 == "circulatory.respiratory" ~ "Circulatory, Respiratory",
    lvl1 == "community" ~ "Community",
    lvl1 == "fitness" ~ "Fitness",
    lvl1 == "immune" ~ "Immune",
    lvl1 == "metabolism" ~ "Metabolism",
    lvl1 == "microbiome" ~ "Microbiome",
    lvl1 == "stress" ~ "Stress"))) %>% # creates new column with nicer names.
  # Level 2 Data tidying
  mutate(lvl2_f = factor(case_when(lvl2 == "abundance"~"Abundance",
    lvl2 == "actinobacteria" ~ "Actinobacteria",
    lvl2 == "aggressivity"~"Agressivity",
    lvl2 == "ammonia.excretion" ~ "Ammonia Excretion",
    lvl2 == "bacteroidetes"~ "Bacteriodetes",
    lvl2 == "blood"~"Blood",
    lvl2 == "body.condition"~"Body Condition",
    lvl2 == "boldness"~"Boldness",
    lvl2 == "brain.histo"~"Brain Histological Abnormalities",
    lvl2 == "burrowing"~"Burrowing",
    lvl2 == "carb.metabolism"~"Carb Metabolism",
    lvl2 == "chemokines.cytokines"~"Chemokines",
    lvl2 == "circulatory"~"Circulatory",
    lvl2 == "detoxification"~"Detoxification",
    lvl2 == "development"~"Development",
    lvl2 == "digestion"~"Digestion",
    lvl2 == "digestive.enzymes"~"Digestive Enzymes",
    lvl2 == "digestive.tract.histo"~"Digestive Tract Histological Abnormalities",
    lvl2 == "diversity"~ "Diversity",
    lvl2 == "feeding"~ "Feeding",
    lvl2 == "firmicutes"~ "Firmicutes",
    lvl2 == "gall.bladder.histo" ~ "Gall Bladder Histological Abnormalities",
    lvl2 == "gen.metabolism"~ "General Metabolism",
    lvl2 == "gill.histo"~ "Gill Histological Abnormalities",
    lvl2 == "gonad.histo"~"Gonad Histological Abnormalities",
    lvl2 == "growth"~ "Growth",
    lvl2 == "immune.cells"~"Immune Cells",
    lvl2 == "immune.other"~"Immune Other ",
    lvl2 == "intestinal.permeability"~"Intestinal Permeability",
    lvl2 == "kidney.histo"~"Kidney Histological abnormalities",
    lvl2 == "lipid.metabolism"~"Lipid Metabolism",
    lvl2 == "liver.histo"~"Liver Histological Abnormalities",
    lvl2 == "liver.kidney.products" ~ "Liver and Kidney Products",
    lvl2 == "locomotion"~"Locomotion",
    lvl2 == "mortality"~"Mortality",
    lvl2 == "nervous.system"~"Nervous System",
    lvl2 == "oxidative.stress"~"Oxidative Stress",
    lvl2 == "photosynthesis"~ "Photosynthesis",
    lvl2 == "proteobacteria"~"Protebacteria",
    lvl2 == "reproduction"~"Reproduction",
    lvl2 == "respiration"~"Respiration",
    lvl2 == "sexhormones"~"Sex Hormones",
    lvl2 == "shoaling"~"Shoaling",
    lvl2 == "stress"~"Stress",
    lvl2 == "vision.system"~"Vision System"))) %>% #Renames for widget
  #Level 3 endpoint tidying
  mutate(lvl3_f = factor(case_when(lvl3 == "11bhsd.mrnaexpression"~"11β HSD mRNA expression",
                                   lvl3 == "17bhsd.mrnaexpression"~"17β HSD mRNA expression",
                                   lvl3 == "1433e.mrnaexpression"~"1433e mRNA expression",
                                   lvl3 == "3bhsd.mrnaexpression"~"3β HSD mRNA expression",
                                   lvl3 == "5ht1.mrnaexpression"~"5ht1 mRNA expression",
                                   lvl3 == "aadd45a.mrnaexpression"~"aadd45a mRNA expression",
                                   lvl3 == "abcb1.mrnaexpression"~"abcb1 mRNA expression",
                                   lvl3 == "abcc.mrnaexpression"~"abcc mRNA expression",
                                   lvl3 == "abcc5.mrnaexpression"~"abcc5 mRNA expression",
                                   lvl3 == "abcd.mrnaexpression"~"abcd mRNA expression",
                                   lvl3 == "abnormality.occurrence"~"Abnormality Occurrence",
                                   lvl3 == "abs.rc"~"Absorption Flux/Reaction Center",
                                   lvl3 == "absorption.efficiency"~"Absorption Efficiency",
                                   lvl3 == "abundance"~"Abundance",
                                   lvl3 == "acc1.mrnaexpression"~"acc1 mRNA expression",
                                   lvl3 == "ace.diversity.index"~"ACE Diversity Index",
                                   lvl3 == "ache.activity"~"AcHE Activity",
                                   lvl3 == "ache.mrnaexpression"~"AcHE mRNA expression",
                                   lvl3 == "acid.phosphatase.activity"~"Acid Phosphatase Activity",
                                   lvl3 == "aco.mrnaexpression"~"aco mRNAexpression",
                                   lvl3 == "acrosomal.integrity"~"Acrosomal Integrity",
                                   lvl3 == "actinobacteria"~"Actinobacteria",
                                   lvl3 == "activity"~"Activity",
                                   lvl3 == "activity.during.feeding"~"Activity During Feeding",
                                   lvl3 == "aeromonas"~"Aeromonas",
                                   lvl3 == "agal.consumption"~"Agal Consumption",
                                   lvl3 == "agression.index"~"Aggression Index",
                                   lvl3 == "ahra.mrnaexpression"~"ahrα mRNA expression",
                                   lvl3 == "ahrb.mrnaexpression"~"ahrβ mRNA expression",
                                   lvl3 == "akt.mrnaexpression"~"akt mRNA expression",
                                   lvl3 == "albumin.con"~"Albumin Concentration",
                                   lvl3 == "albumin.globulin.ratio"~"Albumin to Globulin Ratio",
                                   lvl3 == "algal.density"~"Algal Density",
                                   lvl3 == "alkaline.phosphatase.activity"~"Alkaline Phosphatase Activity",
                                   lvl3 == "aproteobacteria"~"α proteobacteria",
                                   lvl3 == "alp.activity"~"Alkaline Phosphatase Activity",
                                   lvl3 == "alp.con"~"Alkaline Phosphatase Concentration",
                                   lvl3 == "alt.activity"~"Alanine Aminotransferase Activity",
                                   lvl3 == "alt.con"~"Alanine Aminotransferase Concentration",
                                   lvl3 == "amino.acid.trans"~"Amino Acid Transport",
                                   lvl3 == "ammonia.con"~"Ammonia Concentration",
                                   lvl3 == "ampka.mrnaexpression"~"ampka mRNA expression",
                                   lvl3 == "ampkb.mrnaexpression"~"ampkb mRNA expression",
                                   lvl3 == "ampkc.mrnaexpression"~"ampkc mRNA expression",
                                   lvl3 == "amylase.mrnaexpression"~"Amylanse mRNA expression",
                                   lvl3 == "antioxidant.act"~"Antioxidant Activity",
                                   lvl3 == "aox.activity"~"Alternative Oxidase Activity",
                                   lvl3 == "apo.mrnaexpression"~"Apolipoprotein mRNA expression",
                                   lvl3 == "ar.mrnaexpression"~"Androgen Receptor mRNA expression",
                                   lvl3 == "ara.mrnaexpression"~"Androgen Receptor α mRNA expression",
                                   lvl3 == "arb.mrnaexpression"~"Androgen Receptor β mRNA expression",
                                   lvl3 == "area"~"Area",
                                   lvl3 == "area.traveled"~"Area Traveled",
                                   lvl3 == "aspartate.aminotransferase.con"~"Aspartate Aminotransferase Concentration",
                                   lvl3 == "assemblage"~"Assemblage",
                                   lvl3 == "assimilation.efficiency"~"Assimilation Efficiency",
                                   lvl3 == "ast.activity"~"Aspartate Aminotransferase Activity",
                                   lvl3 == "ast.con"~"Aspartate Aminotransferase Concentration",
                                   lvl3 == "attachment"~"Attachment",
                                   lvl3 == "atubulin.mrnaexpression"~"α tubulin mRNA expression",
                                   lvl3 == "atubulin.proteinexpression"~"α tubulin Protein expression",
                                   lvl3 == "bacteroidetes"~"Bacteroidetes",
                                   lvl3 == "bcl2.mrnaexpression"~"bcl2 mRNA expression",
                                   lvl3 == "bfcod.activity"~"BFCOD Activity",
                                   lvl3 == "bile.acid.con"~"Bile Acid Concentration",
                                   lvl3 == "bilirubin.con"~"Bilirubin Concentration",
                                   lvl3 == "biomass"~"Biomass",
                                   lvl3 == "bioturbation"~"Bioturbation",
                                   lvl3 == "body.length"~"Body Length",
                                   lvl3 == "body.mass"~"Body Mass",
                                   lvl3 == "body.width"~"Body Width",
                                   lvl3 == "bproteobacteria"~"βproteobacteria",
                                   lvl3 == "brain.histo"~"Brain Histology",
                                   lvl3 == "brain.mass.index"~"Brain Mass Index",
                                   lvl3 == "brain.water.content"~"Brain Water Content",
                                   lvl3 == "burrow.length"~"Burrow Length",
                                   lvl3 == "burrow.litter"~"Burrow Litter",
                                   lvl3 == "burrow.no"~"Burrow Number",
                                   lvl3 == "burrow.vol"~"Burrow Volume",
                                   lvl3 == "burrow.walldensity"~"Burrow Wall Density",
                                   lvl3 == "burrow.wallweight"~"Burrow Wall Weight",
                                   lvl3 == "burrowing"~"Burrowing",
                                   lvl3 == "ca.mrnaexpression"~"ca mRNA expression",
                                   lvl3 == "calcification"~"Calcification",
                                   lvl3 == "calcium.con"~"Calcium Concentration",
                                   lvl3 == "capture.rate"~"Capture Rate",
                                   lvl3 == "carbohydrate.reserves"~"Carbohydrate Reserves",
                                   lvl3 == "cardiolipin.con"~"Cardiolipin Concentration",
                                   lvl3 == "cas8.mrnaexpression"~"cas8 mRNA expression",
                                   lvl3 == "casp3.mrnaexpression"~"casp3 mRNA expression",
                                   lvl3 == "casp373.mrnaexpression"~"casp373 mRNA expression",
                                   lvl3 == "casp3a.mrnaexpression"~"casp3a mRNA expression",
                                   lvl3 == "casp8.mrnaexpression"~"casp8 mRNA expression",
                                   lvl3 == "casp9.mrnaexpression"~"casp9 mRNA expression",
                                   lvl3 == "caspase3.7.mrnaexpression"~"caspase 3/7 mRNA expression",
                                   lvl3 == "cat.activity"~"Catalase Activity",
                                   lvl3 == "cat.mrnaexpression"~"Catalase mRNA expression",
                                   lvl3 == "cell.autoflourescence"~"Cell Autoflourescence",
                                   lvl3 == "cell.density"~"Cell Density",
                                   lvl3 == "cell.granularity"~"Cell Granularity",
                                   lvl3 == "cell.morphology"~"Cell Morphology",
                                   lvl3 == "cell.necrosis"~"Cell Necrosis",
                                   lvl3 == "cell.size"~"Cell Size",
                                   lvl3 == "cell.viability"~"Cell Viability",
                                   lvl3 == "cellular.energy.allocation"~"Cellular Energy Allocation",
                                   lvl3 == "chg.mrnaexpression"~"Choriogenin mRNA expression",
                                   lvl3 == "chgh.mrnaexpression"~"Choriogenin H mRNA expression",
                                   lvl3 == "chgl.mrnaexpression"~"Choriogenin L mRNA expression",
                                   lvl3 == "chlorophyll"~"Chlorophyll",
                                   lvl3 == "cholesterol.con"~"Cholesterol Concentration",
                                   lvl3 == "chrna1.mrnaexpression"~"chrna1 mRNA expression",
                                   lvl3 == "chymotrypsin.activity"~"Chymotrypsin Activity",
                                   lvl3 == "clearance.rate"~"Clearance Rate",
                                   lvl3 == "clutch.num"~"Number of Clutches",
                                   lvl3 == "clutch.size"~"Clutch Size",
                                   lvl3 == "clutch.size.first"~"First Clutch Size",
                                   lvl3 == "clutch.size.firstthree"~"First Three Clutch Sizes",
                                   lvl3 == "co2.consumption"~"CO2 Consumption",
                                   lvl3 == "condition.index"~"Condition Index",
                                   lvl3 == "congestion"~"Congestion",
                                   lvl3 == "copper.con.hepatopancreas"~"Hepatopancreas Copper Concentration",
                                   lvl3 == "cox.activity"~"Cyclooxygenase Activity",
                                   lvl3 == "coxIV.mrnaexpression"~"Cyclooxygenase IV mRNA expression",
                                   lvl3 == "cpt1.mrnaexpression"~"CPT1 mRNA expression",
                                   lvl3 == "creatine.kinase.con"~"Creatine Kinase Concentration",
                                   lvl3 == "crude.ash"~"Crude Ash",
                                   lvl3 == "crude.protein"~"Curde Protein",
                                   lvl3 == "cs.mrnaexpression"~"Chitin Synthase mRNA expression",
                                   lvl3 == "ctsl.mrnaexpression"~"Cathepsin-L mRNA expression",
                                   lvl3 == "cuznsod.mrnaexpression"~"CuZn Superoxide Dismutase mRNA expression",
                                   lvl3 == "cxcr5.mrnaexpression"~"cxcr5 mRNA expression",
                                   lvl3 == "cyp11.mrnaexpression"~"cyp11 mRNA expression",
                                   lvl3 == "cyp11a2.mrnaexpression"~"cyp11a2 mRNA expression",
                                   lvl3 == "cyp17a1.mrnaexpression"~"cyp17a1 mRNA expression",
                                   lvl3 == "cyp19a.mrnaexpression"~"cyp19a mRNA expression",
                                   lvl3 == "cyp19a2.mrnaexpression"~"cyp19a2 mRNA expression",
                                   lvl3 == "cyp19b.mrnaexpression"~"cyp19b mRNA expression",
                                   lvl3 == "cyp1a.mrnaexpression"~"cyp1a  mRNA expression",
                                   lvl3 == "cyp1a1.mrnaexpression"~"cyp1a1 mRNA expression",
                                   lvl3 == "cyp32.mrnaexpression"~"cyp32 mRNA expression",
                                   lvl3 == "cyp450.proteinexpression"~"cyp450 mRNA expression",
                                   lvl3 == "cyp4an1.mrnaexpression"~"cyp4an1 mRNA expression",
                                   lvl3 == "cyp4c33.mrnaexpression"~"cyp4c33 mRNA expression",
                                   lvl3 == "cyp4c34.mrnaexpression"~"cyp4c34 mRNA expression",
                                   lvl3 == "cytoplasmic.membrane.potential"~"Cytoplasmic Membrane Potential",
                                   lvl3 == "cytotoxicity"~"Cytotoxicity",
                                   lvl3 == "d.lactate"~"D Lactate Concentration",
                                   lvl3 == "dao.activity"~"Diamine Oxidase Activity",
                                   lvl3 == "degranulation"~"Degranulation",
                                   lvl3 == "development"~"Development",
                                   lvl3 == "developmental.abnormalities"~"Developmental Abnormalities",
                                   lvl3 == "dgat.mrnaexpression"~"Diglyceride acyltransferase mRNA expression",
                                   lvl3 == "digestive.tract.histo"~"Digestive Tract Histology",
                                   lvl3 == "dio.rc"~"Energy Dissipated/Reaction Center",
                                   lvl3 == "distance.between.fish"~"Distance Between Fish",
                                   lvl3 == "distance.during.feeding"~"Distance During Feeding",
                                   lvl3 == "diversity"~"Diversity",
                                   lvl3 == "dlac.activity"~"DLac Activity",
                                   lvl3 == "dna.damage"~"DNA Damage",
                                   lvl3 == "dopamine.con"~"Dopamine Concentration",
                                   lvl3 == "egg.size"~"Egg Size",
                                   lvl3 == "embryotoxicity"~"Embryotoxicity",
                                   lvl3 == "emergence"~"Emergence",
                                   lvl3 == "endopeptidase.activity"~"Endopeptidase Activity",
                                   lvl3 == "energy.balance"~"Energy Balance",
                                   lvl3 == "energy.reserves"~"Energy Reserves",
                                   lvl3 == "ep.mrnaexpression"~"ep mRNA expression",
                                   lvl3 == "era.mrnaexpression"~"Estrogen Receptor α mRNA expression",
                                   lvl3 == "erb.mrnaexpression"~"Estrogen Receptor β mRNA expression",
                                   lvl3 == "erk.mrnaexpression"~"erk mRNA expression",
                                   lvl3 == "erod.activity"~"EROD Activity",
                                   lvl3 == "esr2.mrnaexpression"~"esr2 mRNA expression",
                                   lvl3 == "esterase.activity"~"Esterase Activity",
                                   lvl3 == "estradiol.level"~"Estradiol Levels",
                                   lvl3 == "estradiol.testosterone.ratio"~"Estradiol to Testosterone Ratio",
                                   lvl3 == "eto.abs"~"ETO/ABS",
                                   lvl3 == "eto.rc"~"ETO/RC",
                                   lvl3 == "exopeptidase.activity"~"Exopeptidase Activity",
                                   lvl3 == "exploration"~"Exploration",
                                   lvl3 == "f0.fm"~"f0/fm",
                                   lvl3 == "f0.fv"~"f0/fv",
                                   lvl3 == "fabp6.mrnaexpression"~"fabp6 mRNA expression",
                                   lvl3 == "fadd.mrnaexpression"~"fadd mRNA expression",
                                   lvl3 == "fas.mrnaexpression"~"fas mRNA expression",
                                   lvl3 == "fatty.vac"~"Fatty Vacuoles",
                                   lvl3 == "fecundity"~"Fecundity",
                                   lvl3 == "feeding.activity"~"Feeding Activity",
                                   lvl3 == "feeding.rate"~"Feeding Rate",
                                   lvl3 == "feeding.time"~"Feeding Time",
                                   lvl3 == "fertilization"~"Fertilization",
                                   lvl3 == "fertilization.rate"~"Fertilization Rate",
                                   lvl3 == "fertilization.yield"~"Fertilization Yield",
                                   lvl3 == "fibrosis"~"Fiborsis",
                                   lvl3 == "filter.feeding"~"Filter Feeding",
                                   lvl3 == "firmicutes"~"Firmicutes",
                                   lvl3 == "food.consumption"~"Food Consumption",
                                   lvl3 == "foraging.activity"~"Foraging Activity",
                                   lvl3 == "foraging.time"~"Foraging Time",
                                   lvl3 == "foxl2.mrnaexpression"~"fox12 mRNA expression",
                                   lvl3 == "free.fatty.acid.con"~"Free Fatty Acid Concentration",
                                   lvl3 == "fshb.mrnaexpression"~"fshβ mRNA expression",
                                   lvl3 == "fshr.mrnaexpression"~"fshr mRNA expression",
                                   lvl3 == "ftzf1.mrnaexpression"~"ftzf1 mRNA expression",
                                   lvl3 == "fv'.fm'"~"fv'/fm",
                                   lvl3 == "fv.f0"~"fv/f0",
                                   lvl3 == "fv.fm"~"fv/fm",
                                   lvl3 == "fv.fm.sm.tfm"~"fv/fm/sm/tfm",
                                   lvl3 == "gadph.mrnaexpression"~"gadhph mRNA expression",
                                   lvl3 == "gall.bladder.histo"~"Gall Bladder Histology",
                                   lvl3 == "gallery.vol"~"Gallery Volume",
                                   lvl3 == "gcl.mrnaexpression"~"gcl mRNA expression",
                                   lvl3 == "gcl1.mrnaexpression"~"gcl1 mRNA expression",
                                   lvl3 == "gclcs.mrnaexpression"~"gclcs mRNA expression",
                                   lvl3 == "gclcu.mrnaexpression"~"gclcu mRNA expression",
                                   lvl3 == "genera"~"Genera",
                                   lvl3 == "gfap.mrnaexpression"~"gfap mRNA expression",
                                   lvl3 == "ggt.activity"~"Gamma-Glutamyl Transferase Activity",
                                   lvl3 == "ggt.con"~"Gamma-Glutamyl Transferase Concentration",
                                   lvl3 == "gill.histo"~"Gill Histology",
                                   lvl3 == "gk.mrnaexpression"~"gk mRNA expression",
                                   lvl3 == "globulin.con"~"Globulin Concentration",
                                   lvl3 == "glucose.con"~"Glucose Concentration",
                                   lvl3 == "glutamate.con"~"Glutamate Concentration",
                                   lvl3 == "glutathione.con"~"Glutathione Concentration",
                                   lvl3 == "glycogen.con"~"Glycogen Concentration",
                                   lvl3 == "glycogen.deplet"~"Glycogen Depletion",
                                   lvl3 == "gnrh.mrnaexpression"~"gnrh mRNA expression",
                                   lvl3 == "gnrhr.mrnaexpression"~"gnrhr mRNA expression",
                                   lvl3 == "gonad.development.index"~"Gonad Development Index",
                                   lvl3 == "gonad.histo"~"Gonad Histology",
                                   lvl3 == "gonad.regression"~"Gonad Regression",
                                   lvl3 == "gonad.somatic.index"~"Gonad Somatic Index",
                                   lvl3 == "gordonia"~"Gordonia",
                                   lvl3 == "got.activity"~"Glutamic Oxaloacetic Transaminase Activity",
                                   lvl3 == "gpt.activity"~"Glutamic Pyruvic Transaminase Activity",
                                   lvl3 == "gpx.activity"~"Glutathione Peroxidase Activity",
                                   lvl3 == "gpx.mrnaexpression"~"Glutathione Peroxidase mRNA expression",
                                   lvl3 == "gpx4b.mrnaexpression"~"gpx4b mRNA expression",
                                   lvl3 == "gr.activity"~"Glutathione Reductase Activity",
                                   lvl3 == "gr.mrnaexpression"~"Glutathione Reductase mRNA expression",
                                   lvl3 == "granulocyte.con"~"Granulocyte Concentration",
                                   lvl3 == "granulocyte.hyalinocyte.ratio"~"Granulocyte to Hyalinocyte Ratio",
                                   lvl3 == "granulocyte.oxidative.activity"~"Granulocyte Oxidative Activity",
                                   lvl3 == "granulocyte.size"~"Granulocyte Size",
                                   lvl3 == "gross.energy"~"Gross Energy",
                                   lvl3 == "growth"~"Growth",
                                   lvl3 == "growth.rate"~"Growth Rate",
                                   lvl3 == "gs.mrnaexpression"~"Glutathione Synthetase mRNA expression",
                                   lvl3 == "gsh-px.activity"~"Glutathione Peroxidase Activity",
                                   lvl3 == "gsh.activity"~"Glutathione Peroxidase Activity",
                                   lvl3 == "gsh.con"~"Glutathione Peroxidase Concentration",
                                   lvl3 == "gsp.activity"~"Glutathione Peroxidase Activity",
                                   lvl3 == "gst.activity"~"Glutathione S-Transferase Activity",
                                   lvl3 == "gst.mrnaexpression"~"Glutathione S-Transferase mRNA expression",
                                   lvl3 == "gst4.mrnaexpression"~"gst4 mRNA expression",
                                   lvl3 == "gstd.mrnaexpression"~"gstd mRNA expression",
                                   lvl3 == "gstp1.mrnaexpression"~"Glutathione S-Transferase mRNA expression",
                                   lvl3 == "gt.con"~"Glutathione Concentration",
                                   lvl3 == "gtha.mrnaexpression"~"gtha mRNA expression",
                                   lvl3 == "gusb.mrnaexpression"~"gusb mRNA expression",
                                   lvl3 == "gut.mucus.vol"~"Gut Mucus Volume",
                                   lvl3 == "gyrus.size"~"Gyrus Size",
                                   lvl3 == "h2o2.con"~"Hydorgen Peroxide Concentration",
                                   lvl3 == "h3.mrnaexpression"~"h3 mRNA expression",
                                   lvl3 == "haemocyanin.con"~"Haemocyanin Concentration",
                                   lvl3 == "hemocyte.con"~"Hemocyte Concentration",
                                   lvl3 == "haemolymph.con"~"Haemolymph Concentration",
                                   lvl3 == "hatching.success"~"Hatching Success",
                                   lvl3 == "hdl.con"~"HDL Concentration",
                                   lvl3 == "heart.rate"~"Heart Rate",
                                   lvl3 == "hepatic.somatic.index"~"Hepatic Somatic Index",
                                   lvl3 == "hepatopancreas.water.con"~"Hepatopancreas Water Concentration",
                                   lvl3 == "hex.mrnaexpression"~"hex mRNA expression",
                                   lvl3 == "hk.mrnaexpression"~"hk mRNA expression",
                                   lvl3 == "hk1.mrnaexpression"~"hk1 mRNA expression",
                                   lvl3 == "ho1.mrnaexpression"~"ho1 mRNA expression",
                                   lvl3 == "hsp70.mrnaexpression"~"hsp70 mRNA expression",
                                   lvl3 == "hsp90.mrnaexpression"~"hsp90 mRNA expression",
                                   lvl3 == "hyalinocyte.size"~"Hyalinocyte Size",
                                   lvl3 == "hylaniocyte.oxidative.activity"~"Hylaniocyte Oxidative Activity",
                                   lvl3 == "id.mrnaexpression"~"Isocitrate Dehydrogenase mRNA expression",
                                   lvl3 == "idh.activity"~"Isocitrate Dehydrogenase Activity",
                                   lvl3 == "idp.mrnaexpression"~"idp mRNA expression",
                                   lvl3 == "ifn.mrnaexpression"~"Interferon mRNA expression",
                                   lvl3 == "ifny.mrnaexpression"~"Interferon y mRNA expression",
                                   lvl3 == "igm.con"~"Immunoglobulin M Concentration",
                                   lvl3 == "igm.mrnaexpression"~"Immunoglobulin M mRNA expression",
                                   lvl3 == "il10.mrnaexpression"~"Interleukin 10 mRNA expression",
                                   lvl3 == "il17.mrnaexpression"~"Interleukin 17 mRNA expression",
                                   lvl3 == "il1a.mrnaexpression"~"Interleukin 1α mRNA expression",
                                   lvl3 == "il1b.mrnaexpression"~"Interleukin 1β mRNA expression",
                                   lvl3 == "il413a.mrnaexpression"~"Interleukin 413α mRNA expression",
                                   lvl3 == "il6.mrnaexpression"~"Interleukin 6 mRNA expression",
                                   lvl3 == "il8.mrnaexpression"~"Interluekin 8 mRNA expression",
                                   lvl3 == "ila.con"~"Interleukin 1α Concentration",
                                   lvl3 == "immobilization"~"Immobilization",
                                   lvl3 == "inflam.infiltrate"~"Inflammatory Filtrate",
                                   lvl3 == "ingestion.rate"~"Ingestion Rate",
                                   lvl3 == "inhibitory.rate"~"Inhibitory Rate",
                                   lvl3 == "instar.develop.time"~"Instar Development Time",
                                   lvl3 == "intermolt.time"~"Intermolt Time",
                                   lvl3 == "intestinal.ca.con"~"Intestinal Calcium Concentration",
                                   lvl3 == "ion.exch.ca"~"Ion Exchange (Calcium)",
                                   lvl3 == "ion.exch.k"~"Ion Exchange (Potassium)",
                                   lvl3 == "ion.exch.na"~"Ion Exchange (Sodium)",
                                   lvl3 == "ion.flow"~"Ion Flow",
                                   lvl3 == "ion.permeability"~"Ion Permeability",
                                   lvl3 == "ion.trans"~"Ion Transport",
                                   lvl3 == "jaw.tissue.damage"~"Jaw Tissue Damage",
                                   lvl3 == "jnk.mrnaexpression"~"jnk mRNA expression",
                                   lvl3 == "jump.freq"~"Jump Frequency",
                                   lvl3 == "jump.height"~"Jump Height",
                                   lvl3 == "kidney.histo"~"Kidney Histology",
                                   lvl3 == "labilization.period"~"Labilization Period",
                                   lvl3 == "lactate.con"~"Lactate Concentration",
                                   lvl3 == "ldh.activity"~"Lactate Dehydrogenase Activity",
                                   lvl3 == "ldh.con"~"Lactate Dehydrogenase Concentration",
                                   lvl3 == "ldl.con"~"LDL Concentration",
                                   lvl3 == "leaf.growth.rate"~"Leaf Growth Rate",
                                   lvl3 == "length"~"Length",
                                   lvl3 == "leukocyte.con"~"Leukocyte Concentration",
                                   lvl3 == "lhb.mrnaexpression"~"Leutinizing Hormone β mRNA expression",
                                   lvl3 == "lhr.mrnaexpression"~"Leutinizing Hormone Receptor mRNA expression",
                                   lvl3 == "lifespan"~"Lifespan",
                                   lvl3 == "light.capture"~"Light Capture",
                                   lvl3 == "light.dark.activity"~"Light/Dark Activity",
                                   lvl3 == "line.crossing"~"Line Crossing",
                                   lvl3 == "lipase.activity"~"Lipase Activity",
                                   lvl3 == "lipase.con"~"Lipase Concentration",
                                   lvl3 == "lipid.content"~"Lipid Content",
                                   lvl3 == "lipid.membrane.con"~"Lipid Membrane Concentration",
                                   lvl3 == "lipid.perox"~"Lipid Peroxidation",
                                   lvl3 == "lipid.storage.con"~"Lipid Storage Concentration",
                                   lvl3 == "lipofuscin.accum"~"Lipofuscin Accumulation",
                                   lvl3 == "liver.histo"~"Liver Histology",
                                   lvl3 == "liver.protein"~"Liver Protein",
                                   lvl3 == "lymphocyte.con"~"Lymphocyte Concentration",
                                   lvl3 == "lys.mrnaexpression"~"Lysozyme mRNA expression",
                                   lvl3 == "lysosomal.membrane.stab"~"Lysosomal Membrane Stability",
                                   lvl3 == "lysozyme.activity"~"Lysozyme Activity",

>>>>

#Import packages
library(tidyverse) 
library(wesanderson)
library(pheatmap)
library(RColorBrewer)
library(ggpubr)
library(ssdtools)
library(scales)

library(ggdark)
library(ggsci)

#Import Data
aoc_setup <- readRDS("aoc_setup.RDS")
aoc_z <- readRDS("aoc_z.RDS")
```

# Figure 1

```{r}

#Select particle characteristics
selected_variables <- aoc_setup %>% 
  dplyr::select(
    size_f,
    shape_f,
    poly_f,
    density.reported.estimated,
    charge,
    functional.group,
    particle.behavior,
    weather.biofoul) %>% 
  filter(size_f != "Not Reported")

selected_variables$shape_f[selected_variables$shape_f == "Not Reported" ] <- NA
selected_variables$poly_f[selected_variables$poly_f == "Not Reported" ] <- NA
selected_variables$density.reported.estimated[selected_variables$density.reported.estimated == "estimated" ] <- NA
selected_variables$particle.behavior[selected_variables$particle.behavior == "Not Evaluated" ] <- NA
selected_variables$weather.biofoul[selected_variables$weather.biofoul == "N" ] <- NA

CompletenessSummary_size <- selected_variables %>%
  group_by(size_f) %>% 
  summarise_all((name = ~sum(is.na(.))/length(.))) %>% 
  mutate(across(is.numeric,~round(., 2))) %>% 
  mutate(across(is.numeric, ~100 *(1 -.))) %>% 
  rename("Size Category" = size_f, "Shape" = shape_f, "Polymer" = poly_f, "Density" = density.reported.estimated,
         "Charge" = charge, "Functional Group" = functional.group, "Particle Behavior" = particle.behavior,
         "Weathering" = weather.biofoul)

#Heatmap

#Transpose data
transposed_size <- as.data.frame(t(as.matrix(CompletenessSummary_size[2:8]))) %>% #1 is category, 2-6 are variables
  arrange('1nm < 100nm')
#Reassign column names
colnames(transposed_size) <- c("1nm < 100nm", "100nm < 1µm", "1µm < 100µm", "100µm < 1mm", "1mm < 5mm")
#Format as matrix
MissingMatrix_size <- data.matrix(transposed_size)
#build heatmap
map <- pheatmap(MissingMatrix_size,
         main = "Particle Characteristics Reported", #title
         fontsize = 12,
         angle_col = 0,
         cluster_rows = FALSE, cluster_cols = FALSE,
         display_numbers = TRUE,
         fontsize_number = 12,
         number_color = "black",
         number_format = "%.0f%%",
         treeheight_row = 0, treeheight_col = 0, 
         color = c("#EEFFFF", "#BAFFFF", "#88E7FF", "#55B4CC", "#3B9AB2", "#228199"))

ggsave(filename = "Figure1.jpg",
       path = "App_Nonessential/TeamX_Manuscript_Figures/",
       plot = map, width = 8, height = 4, units = "in")
